Dynamics of Laterally Propagating Flames in X-ray Bursts. II. Realistic Burning \& Rotation

### 2020-12-23 xrb2/paper.tex
updated flame speeds table
Updated notes and density phase plot caption

%======================================================================
% Numerical Approach
%======================================================================
\section{Numerical Approach}\label{Sec:numerics}
\MarginPar{mz}

@@

\begin{figure}[t]
\centering
\plotone{time_series_1000}
\caption{\label{fig:time_series_1000} Time series of {\tt F1000} showing $\bar{A}$.}
\end{figure}
\MarginPar{update both the abar figures to only show 50 ms and 100 ms snapshots}

@@

\begin{figure}[t]
\centering
\plotone{time_series_enuc_1000}
\caption{\label{fig:time_series_enuc_1000} Time series of {\tt F1000} showing $\dot{e}_\mathrm{nuc}$.}
\end{figure}
\MarginPar{update both the abar figures to only show 50 ms and 100 ms snapshots}

@@

Burning in the {\tt F500} and {\tt F1000} runs is concentrated in a dense region with circular motion. Figure \ref{fig:urho} compares the horizontal $x$-velocity $u$, density $\rho$ and the nuclear energy generation rate $\dot{e}_{\rm nuc}$ for {\tt F250}, {\tt F500}, and {\tt F1000}. Most of the burning for each of the simulations occurs in a high density region $\rho > 3 \times 10^5 {\rm g/cm^3}$. The fluid in this dense, high energy generation region undergoes vortical motion, shown in the Figure \ref{fig:uv} phase plots comparing $u$, $v$ and $\dot{e}_{\rm nuc}$. From the previous plots (see: streamlines?) \MarginPar{NF: which plots?}, this most likely corresponds to the leading edge of the flame where fresh fuel is being entrained. This feature is not developed in the 250~Hz flame; it could potentially develop at later times, or the flame could just fizzle out.

@@

\begin{figure}[t]
    \centering
    \plotone{urho_plot_0_1}{}
    \caption{\label{fig:urho}Phase plot of the horizontal $x$-velocity $u$, density $\rho$ and the nuclear energy generation rate $\dot{e}_{\rm nuc}$ for the 250, 500 and 1000~Hz runs.}
\end{figure}

@@

MZ: lateral profiles of X vs distance behind the flame; 
vertical profiles of the atmosphere behind the flame---how does it compare to isentropic?

what is the composition on the photosphere across the flame

shape of flame, amount of mixing (e.g. it looks like slower rotation rates have less mixed flames as the hurricane is less strong.)

Don: look at ratio of enuc to e?

@@

\begin{deluxetable}{lrrr}
	\tablecaption{\label{table:flame_speeds} Flame speed and acceleration values measured for each simulation. $s_0$ is the speed at $t = 0$. The initial flame velocities and accelerations are derived from a quadratic least-squares fit to each of the datasets for times $t \gtrsim 0.02~\mathrm{s}$.}
	\tablehead{\colhead{run} & \colhead{$s_0$ (cm s$^{-1}$)} & \colhead{$a$ (cm s$^{-2}$)}} 
	\startdata
	{\tt F1000}     & $(3.41 \pm 0.01) \times 10^5$ & $(-1.03 \pm 0.13) \times 10^5$ \\
	{\tt F500}      & $(3.08 \pm 0.01) \times 10^5$ & $(5.41 \pm 0.19) \times 10^5$ \\
	{\tt F500\_2E8} & $(3.76 \pm 0.02) \times 10^5$ & $(1.74 \pm 0.17) \times 10^5$ \\
	{\tt F500\_3E8} & $(5.29 \pm 0.10) \times 10^5$ & $(3.57 \pm 0.02) \times 10^7$ \\
	\enddata
	%
\end{deluxetable}

>>>>

%======================================================================
% Numerical Approach
%======================================================================
\section{Numerical Approach}\label{Sec:numerics}

@@

\begin{figure}[t]
\centering
\plotone{time_series_1000}
\caption{\label{fig:time_series_1000} Time series of {\tt F1000} showing $\bar{A}$.}
\end{figure}

@@

\begin{figure}[t]
\centering
\plotone{time_series_enuc_1000}
\caption{\label{fig:time_series_enuc_1000} Time series of {\tt F1000} showing $\dot{e}_\mathrm{nuc}$.}
\end{figure}

@@

Burning in the {\tt F500} and {\tt F1000} runs is concentrated in a dense region with circular motion. Figure \ref{fig:urho} compares the horizontal $x$-velocity $u$, density $\rho$ and the nuclear energy generation rate $\dot{e}_{\rm nuc}$ for {\tt F250}, {\tt F500}, and {\tt F1000}. Most of the burning for each of the simulations occurs in a high density region $\rho > 3 \times 10^5 {\rm g/cm^3}$. The fluid in this dense, high energy generation region undergoes vortical motion, shown in the Figure \ref{fig:uv} phase plots comparing $u$, $v$ and $\dot{e}_{\rm nuc}$. From the previous plots (see: streamlines?) \MarginPar{NF: need to add streamline plots?}, this most likely corresponds to the leading edge of the flame where fresh fuel is being entrained. This feature is not developed in the 250~Hz flame; it could potentially develop at later times, or the flame could just fizzle out.

@@

\begin{figure}[t]
    \centering
    \plotone{urho_plot_0_1}{}
    \caption{\label{fig:urho}Phase plot of the horizontal $x$-velocity $u$, density $\rho$ and the nuclear energy generation rate $\dot{e}_{\rm nuc}$ for the 250, 500 and 1000~Hz runs. The slightly lower $\dot{e}_{\rm nuc}$ values along the $u = 0$ axis are most likely a numerical artifact related to the density gradient setup and finite resolution of these simulations.}
\end{figure}

@@

\MarginPar{Mike wants to check vertical profiles of atmosphere behind flame}

@@

\begin{deluxetable}{lrrr}
	\tablecaption{\label{table:flame_speeds} Flame speed and acceleration values measured for each simulation. $s_0$ is the speed at $t = 0$. The initial flame velocities and accelerations are derived from a quadratic least-squares fit to each of the datasets for times $t \gtrsim 0.02~\mathrm{s}$.}
	\tablehead{\colhead{run} & \colhead{$s_0$ (cm s$^{-1}$)} & \colhead{$a$ (cm s$^{-2}$)}} 
	\startdata
	{\tt F1000}     & $(3.38 \pm 0.11) \times 10^5$ & $(-0.43 \pm 1.57) \times 10^5$ \\
	{\tt F500}      & $(2.66 \pm 0.27) \times 10^5$ & $(10.97 \pm 3.22) \times 10^5$ \\
	{\tt F500\_2E8} & $(3.98 \pm 0.19) \times 10^5$ & $(-1.56 \pm 2.63) \times 10^5$ \\
	{\tt F500\_3E8} & $(-4.56 \pm 2.92) \times 10^5$ & $(3.39 \pm 0.60) \times 10^7$ \\
	\enddata
	%
\end{deluxetable}
